---
title: "Class Notes"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 1
    #code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```

## Class 1 (1/28/19)
Version control: time capsule of every change you’ve made to you files 	-copy of every time you’ve saved a file 

Making a change and pushing it to web: 
	-when you change in Studio, if you look at gitbub desktop, you can    see what has been changed 
	-make sure you have saved your work in r studio 
	-go to getup and select things you want to save 

Option+command+I -> tell r markdown that you are now writing R code

Control+enter -> put cursor on the first line of your code and it will run

Equals sign in r means something else! use <- instead to assign variables
	-You can put numbers or text into variables

You can see the variables that you have assigned in your “environments” table on the top right corner of R-studio 

Clear variables: session -> clear workspace 

You can turn on/off R code in your website: set an option “eval” and the {r} place 
	{r, eval=FALSE} and the code will not be evaluated. You are then able to build your website even though your code is not running correctly. 

Stack exchange: forum to answer questions about R

## Class 3 (2/11/19)

###***Creating an R Package***
What are packages? A series of R functions
	-ex: making beautiful graphs 
	
CRAN: cloud based repository, that is shared across the world, society of R packages 

TidyVerse: data analysis package

Loading a package
  -check the package button 
  -or library(packagename)
  
Functions: creates a series of steps in one simple function 
  -takes an input, does something, returns output 

####***Format of writing a function:***
```{r}
name_of_function <- function(input){
  #body of code 
  return(output)
}
```

####***Example function:***
```{r}
add_one <-function(x){
  return(x+1)
}

add_one(6)
```
Breaking down the steps of your function using comments can ease in writing and understand where you went wrong. 

You can also write a function that does not take any inputs

####***Rolling a Dice example (no input)***
```{r}
sample(1:6,1) #using an instinsic to do that same thing a function will do 

roll_dice <- function(){
  return(sample(1:6,1))
}

#This function does the same thing as the instrinsic 
```
You can type in simply the name of a function and it will show you the steps. This is when you don't use the parenthesis.

Return: important because that is what will come out of the function. You can tell it to return anything you like 

Print vs return: 
  -Print: prints whatever to the console, but does not return the       output of a function
  -Return: allows the value to exist in memory which can also be       placed into another variable 
  
Making a package: 
  1) make a new project 
  2) new directory 
  3) R package 
  4) Choose "subdirectory" and make sure you know where you are          storing it 
  
Two folders "r" and "man"
  -"r": containing "hello.R", which contains a simple function which        prints "Hello, World"
  -"man": what you write in this section, is what will show up on the         help page when you ?funcition

New Script, save it to R folder 
  -Then you are able to create functions to combine which makes your    package. 
  -Every function should be a separate .R folder 






