---
title: "Class Notes"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 1
    #code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```

## Class 1 (1/28/19)
Version control: time capsule of every change you’ve made to you files 	-copy of every time you’ve saved a file 

Making a change and pushing it to web: 
	-when you change in Studio, if you look at gitbub desktop, you can    see what has been changed 
	-make sure you have saved your work in r studio 
	-go to getup and select things you want to save 

Option+command+I -> tell r markdown that you are now writing R code

Control+enter -> put cursor on the first line of your code and it will run

Equals sign in r means something else! use <- instead to assign variables
	-You can put numbers or text into variables

You can see the variables that you have assigned in your “environments” table on the top right corner of R-studio 

Clear variables: session -> clear workspace 

You can turn on/off R code in your website: set an option “eval” and the {r} place 
	{r, eval=FALSE} and the code will not be evaluated. You are then able to build your website even though your code is not running correctly. 

Stack exchange: forum to answer questions about R

## Class 3 (2/11/19)

###***Creating an R Package***
What are packages? A series of R functions
	-ex: making beautiful graphs 
	
CRAN: cloud based repository, that is shared across the world, society of R packages 

TidyVerse: data analysis package

Loading a package
  -check the package button 
  -or library(packagename)
  
Functions: creates a series of steps in one simple function 
  -takes an input, does something, returns output 

####***Format of writing a function:***
```{r}
name_of_function <- function(input){
  #body of code 
  return(output)
}
```

####***Example function:***
```{r}
add_one <-function(x){
  return(x+1)
}

add_one(6)
```
Breaking down the steps of your function using comments can ease in writing and understand where you went wrong. 

You can also write a function that does not take any inputs

####***Rolling a Dice example (no input)***
```{r}
sample(1:6,1) #using an instinsic to do that same thing a function will do 

roll_dice <- function(){
  return(sample(1:6,1))
}

#This function does the same thing as the instrinsic 
```
You can type in simply the name of a function and it will show you the steps. This is when you don't use the parenthesis.

Return: important because that is what will come out of the function. You can tell it to return anything you like 

Print vs return: 
  -Print: prints whatever to the console, but does not return the       output of a function
  -Return: allows the value to exist in memory which can also be       placed into another variable 
  
Making a package: 
  1) make a new project 
  2) new directory 
  3) R package 
  4) Choose "subdirectory" and make sure you know where you are          storing it 
  
Two folders "r" and "man"
  -"r": containing "hello.R", which contains a simple function    which prints "Hello, World"
  -"man": what you write in this section, is what will show up on the help page when you ?funcition

New Script, save it to R folder 
  -Then you are able to create functions to combine which makes your    package. 
  -Every function should be a separate .R folder 


Loading packages from R 
"devtools"


## Class 4 2/25
Using ggplot2 to make a graph 
  -learning how to code to create these graphs 

Data Frames: a type of format 
-work flow in R: get data from somewhere, put it into R and use it
-there are a number of different formats to do that. Data frame is one type of format 
  -many libraries/functions are made to be used with data frame
-to use ggplot2 you must first put it in a data frame

What is a data frame? 
-similar to an excel spreadsheet with rows and columns 

### Making a data frame: 
```{r}
a <- data.frame()
```
^creates an empty data frame without anything in it 
-helpful to have meaningful names of columns/rows

-rows are generally different participants data, columns are DV or IV

```{r}
Names <- c("Peter", "Paul", "Mary", NA)
Ages <- c(1000,1200,100,50)
Sex <- c("M", "M", "F", NA)


my_dataframe <- data.frame(Names,
                           Ages,
                           Sex)
#data does not need to be stacked as above, but it eases in reading 
#you are adding on new columns as you add information within the parenthesis 
```
-You need to make sure that you always have the same number of rows and columns 
  -the way to get around that is to include an NA section for Names and Sex as displayed above 

-You can call out specific columns of a data frame by using:
nameofdatafram$nameofcolumn
  -when you call out the column in this way, you are also given the levels of the column which shows the levels of the variable 
  

### Making a scatterplot 
```{r}
# Create dataframe
a <- c(1,2,3,2,3,4,5,4)
b <- c(4,3,4,3,2,1,2,3)
plot_df <- data.frame(a,b)

# basic scatterplot
ggplot(plot_df, aes(x=a,y=b))+
  geom_point()
```

ggplot2 syntax: 
1) first load by selecting the check mark net to it or doing library(ggplot2)
2) ggplot(yourdataframe)
3) then you have to tell it where it put the different variables 
  ggplot(yourdataframe, aes(x=,y=)). This sets up a canvas. Makes a plot without any of the values. You then add layers to your canvas 
4)ggplot(yourdataframe, aes(x=,y=)) + geom_point()
  -geoms are additionals you can add to the graph
  
```{r}
# customize, add regression line
ggplot(plot_df, aes(x=a,y=b))+
  geom_point(size=2)+
  #adds points, which you can change the size of by selecting size
  geom_smooth(method=lm)+
  #adds linear regression 
  coord_cartesian(xlim=c(0,7),ylim=c(0,10))+
  #controls the range, specifically setting x and y limits 
  xlab("x-axis label")+
  ylab("y-axis label")+
  #changes the x and y axis labels 
  ggtitle("I made a scatterplot")+
  #adds a title 
  theme_classic(base_size=12)+
  #getting rid of the gray background, makes it a classic white background. base size is the size of the font on the graph
  theme(plot.title = element_text(hjust = 0.5))
#default title is left sided. this command centers the title 
```

ggplot2 makes solving annoying proglems easy
-resizing: will ensure that you are never changing the font/graph size -> final product is precise

### Bar graph
```{r}
#Create a dataframe
factor_one <- as.factor(c("A","B","C"))
dv_means <- c(20,30,40)
dv_SEs   <- c(4,3.4,4)
plot_df <- data.frame(factor_one,
                      dv_means,
                      dv_SEs)

# basic bar graph

ggplot(plot_df, aes(x=factor_one,y=dv_means))+
  geom_bar(stat="identity")
#aes: you can designate what you want to go across the x and y axis 
#geom_bar adds the bars to the graph "canvas"
#you always start is putting in the data to the graph and designating the axis. Then you are drawing on top the additional formatting (bars, lines points etc)
#stat=identity -> necessary, not running any manipulation
```

### Adding error bars and further customizing graphs 
```{r}
ggplot(plot_df, aes(x=factor_one,y=dv_means))+
  geom_bar(stat="identity")+
  geom_errorbar(aes(ymin=dv_means-dv_SEs,
                    ymax=dv_means+dv_SEs),
                width=.2)+
  #adds error bars. Must tell what min and max of error bars
  coord_cartesian(ylim=c(0,100))+
  xlab("x-axis label")+
  ylab("y-axis label")+
  ggtitle("I made a bar graph")+
  theme_classic(base_size=12)+
  theme(plot.title = element_text(hjust = 0.5))
```

### Graph a factorial design on a bar graph 
```{r}
#Create a dataframe
factor_one <- rep(as.factor(c("A","B","C")),2)
factor_two <- rep(as.factor(c("IIA","IIB")),3)
dv_means <- c(20,30,40,20,40,40)
dv_SEs   <- c(4,3.4,4,3,2,4)
plot_df <- data.frame(factor_one,
                      factor_two,
                      dv_means,
                      dv_SEs)

# basic bar graph

ggplot(plot_df, aes(x=factor_one,y=dv_means,
                    group=factor_two,
                    color=factor_two,
                    fill=factor_two))+
  #aes getings longer. color -> boarder color, but fill -> is color of the bar itself 
  geom_bar(stat="identity", position="dodge")
#position="dodge" makes two smaller bars for each factor instead of the factors on top of each other 
#if you want to change the colors of the bars, do that here
```

### 3 Factor 
```{r}
#Create a dataframe
factor_one <- rep(rep(as.factor(c("A","B","C")),2),2)
factor_two <- rep(rep(as.factor(c("IIA","IIB")),3),2)
factor_three <- rep(as.factor(c("IIIA","IIIB")),each=6)
dv_means <- c(20,30,40,20,40,40,
              10,20,50,50,10,10)
dv_SEs   <- c(4,3.4,4,3,2,4,
              1,2,1,2,3,2)
plot_df <- data.frame(factor_one,
                      factor_two,
                      factor_three,
                      dv_means,
                      dv_SEs)

# basic bar graph

ggplot(plot_df, aes(x=factor_one,y=dv_means,
                    group=factor_two,
                    color=factor_two))+
  geom_bar(stat="identity", position="dodge")+
  facet_wrap(~factor_three)
#this separates the graphs by whatever you tell it to 

```


To change the way the IV is repeated, add each=2
  -changes it from sally bob cathy sally bob cathy to sally sally bob bob cathy cathy 
