---
title: "Data Wrangle"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 2
    #code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```

## Loading libraries 

```{r}
library(data.table)
library(dplyr)
library(ggplot2)


names <- list.files(path="FlankerData")

headers <- c("stimulus","congruency","proportion",
                 "block","condition","dualtask","unknown",
                 "stimulusonset","responsetime","response","subject")

#Making empty data frame, make loop loading data into data frame 
alldata<-data.frame()

for(i in names){
  onesubject <- fread(paste("FlankerData/",i, sep=""))
  names(onesubject) <- headers
  onesubject$subject <- rep(i,dim(onesubject)[1])
  onesubject <- cbind(onesubject, trial= 1:dim(onesubject)[1])
  alldata <- rbind(alldata,onesubject)
}

```

## Pre-processing

### get accuracy for each trial

```{r, eval=FALSE}

centerletter <- unlist(lapply(strsplit(alldata$stimulus,""),
                           FUN=function(x)unlist(x)[2]))

centerletter <- unlist(strsplit(alldata$stimulus,""))
everyothernumber <- seq(1,12672, 2)

#looping to find center letter?
#for (i in length(centerletter)) {
#center_letter1 <- i[-everyothernumber]


alldata <- cbind(alldata,centerletter)
alldata <- alldata %>%
              mutate(response = tolower(response),
                     centerletter = tolower(centerletter),
                     accuracy = response==centerletter)

}
```

### Get Reaction time on each trial

```{r, eval=FALSE}

alldata <- alldata %>%
              mutate(RT = as.integer(responsetime - stimulusonset))

#all_data <- as.integer(all_data$response_time-all_data$rstimulus_onset)


```


## Checks

```{r, eval=FALSE}

#Finding the numbers of congruent/incongruent trials 
check <- alldata$congruency 

numbersofI <- 0
numbersofC <- 0

for (i in check) {
  if (i=I) {
    numbersofI <- numbersofI + 1
  }
  if (i=C) {
    numbersofC <- numbersofC + 1
  }
}
  
```


### Exclusion

```{r, eval=FALSE}
slowdata <- alldata %>%
              filter(RT < 2000)
```

## Analysis

### Reaction Time analysis

1. Get the individual subject mean reaction times for **correct** congruent and incongruent trials.

```{r, eval=FALSE}
meanRTs <- restricted %>%
                    filter(accuracy == TRUE) %>%
                    group_by(subject,congruency) %>%
                    summarise(meanRTs = mean(RT))
```


2. Get the overall mean RTs and SEMs (standard errors of the mean) for the congruent and incongruent condition. Make a table and graph.

```{r, eval=FALSE}
congruencymeans <- meanRTs %>%
                      group_by(congruency) %>%
                      summarise(meanRTs = mean(meanRTs),
                                SEM = sd(meanRTs)/sqrt(length(meanRTs)))
knitr::kable(congruencymeans)
ggplot(congruencymeans, aes(x=congruency,y=meanRTs,
                             fill=congruency))+
  geom_bar(stat="identity")+
  theme_classic(base_size=12)+
  ylab("Mean Reaction Time (ms)")+
  geom_errorbar(aes(ymin=meanRTs-SEM,
                    ymax=meanRTs+SEM),
                position=position_dodge(width=0.9),
                width=.2,
                color="black")+
  coord_cartesian(ylim=c(700,1000))
  
  
```

3. Compute the flanker effect for each subject, taking the difference between their mean incongruent and congruent RT. Then plot the mean flanker effect, along with the SEM of the mean flanker effect


```{r, eval=FALSE}

flankermeans <- subjectmeanRTs[subjectmeanRTs$congruency=="I",]$meanRTs - 
  subjectmeanRTs[subjectmeanRTs$congruency=="C",]$meanRTs
flanker <- data.frame(dv = "flanker effect",
                         flankermean1 = mean(flankermeans),
                         SEM = sd(flankermeans)/sqrt(length(flankermeans)))

ggplot(flanker_df, aes(x=dv, y=flankermean1))+
  geom_bar(stat="identity")+
  theme_classic(base_size=12)+
  ylab("Flanker Effect")+
  geom_errorbar(aes(ymin=flankermean1-SEM,
                    ymax=flankermean1+SEM),
                position=position_dodge(width=0.9),
                width=.2,
                color="black")
  
```


### Exploratory analysis

```{r, eval=FALSE}
previous_congruency <- c(0,alldata$congruency[1:(length(alldata$congruency)-1)])
sequence_subjects <- alldata %>%
                      mutate(n1_congruency = previous_congruency) %>%
                      filter(trial > 1,
                             RT < 2000,
                             accuracy == TRUE) %>%
                      group_by(subject,congruency,n1_congruency) %>%
                      summarise(meanRT = mean(RT))
sequence_means <- sequence_subjects %>%
                    group_by(congruency,n1_congruency) %>%
                    summarise(mean_RT = mean(meanRT),
                              SEM = sd(meanRT)/sqrt(length(meanRT)))
                      
knitr::kable(sequence_means)
ggplot(sequence_means, aes(x=n1_congruency, y=mean_RT,
                           group=congruency,
                           fill=congruency))+
  geom_bar(stat="identity", position="dodge")+
  theme_classic(base_size=12)+
  ylab("Mean RT (ms")+
  geom_errorbar(aes(ymin=mean_RT-SEM,
                    ymax=mean_RT+SEM),
                position=position_dodge(width=0.9),
                width=.2,
                color="black")+
  coord_cartesian(ylim=c(600,900))

```




