---
title: "Easy Problems"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 2
    #code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```

### Problem 1
Do simple math with numbers, addition, subtraction, multiplication, division
```{r}

1+1
6-5
9*0
10/5

```

### Problem 2
Put numbers into variables, do simple math on the variables 
```{r, eval=FALSE}

a <- 1
b <- 3

a+b
b-a
a*b
b/a

c <- 5

a+b+c
```

### Problem 3
Write code that will place the numbers 1 to 100 separately into a variable using for loop. Then, again using the seq function.
```{r}
Numbers <-seq(1:100)

for (i in 1:length(Numbers)){
  print(Numbers[[i]])
}

```

### Problem 4
Find the sum of all the integer numbers from 1 to 100
```{r}
values <- seq(1:100)
sum(values)
```

### Problem 5
Write a function to find the sum of all integers between any two values.
```{r}
summing <- function(x){
  a <- seq(a:b)
  x <- sum(a)
  return(x)
}
```

### Problem 6
List all of the odd numbers from 1 to 100.
```{r}
q <- seq(from=1, to=100, by=2)
```

### Problem 7
List all of the prime numbers from 1 to 1000.
```{r, eval=FALSE}
Prime_Numbers <-(1:1000)
a <- Prime_Numbers%%Prime_Numbers
if (a==0)
  a <- Prime_Numbers
if (a/=0)
  b <- Prime_Numbers
print(b)

```

### Problem 8
Generate 100 random numbers
```{r}
runif(100)
```

### Problem 9 
Generate 100 random numbers within a specific range
```{r}
runif(100,0,100)
```

### Problem 10 
Write your own functions to give descriptive statistics for a vector variable storing multiple numbers. Write functions for the following without using R intrinsics: mean, mode, median, range, standard deviation
```{r}
meaning <- function(a) {
   for(i in 1:a) {
      b<-sum(a)
      localmean<-b/length(a)
      print(b)
   }
}
```

### Problem 11
Count the number of characters in a string variable
```{r}
a <- "adskfjhkadsjfh"
strsplit(a,split="")
b <- length(a[[1]])
```

### Problem 12
Count the number of words in a string variable
```{r}
a <- "count the number of words in this sentence"

b <- strsplit(a, split=" ")

length(b[[1]])

```

### Problem 13 
Count the number of sentences in a string variable

```{r}
a <- "This is one sentence. This is another sentence as well. Here is the third sentence. But wait there is also a fourth sentence."

b <- strsplit(a, split="[.]")

length(b[[1]])

```

### Problem 14
Count the number of times a specific character occurs in a string variable
```{r}
a <- "abcabbccaaabbbbc"

b <- strsplit(a, split="a")

length(b[[1]])
```

### Problem 15 
Do a logical test to see if one word is found within the text of another string variable.
```{r}

test_word <- "hello"

test_sentence <- c("is", "the", "word", "hello", "in", "this", "sentence")

test_word%in%test_sentence


```

### Problem 16 
Put the current computer time in milliseconds into a variable
```{r}
print(as.numeric(Sys.time())*1000, digits=15)
```

### Problem 17
Measure how long a piece of code takes to run by measuring the time before the code is run, and after the code is run, and taking the difference to find the total time
```{r, eval=FALSE}
sleep_for_a_minute <- function(x) { Sys.sleep(60) }

start_time <- Sys.time(x)
sleep_for_a_minute(x)
end_time <- Sys.time(x)

end_time - start_time

```

### Problem 18
Read a .txt file or .csv file into a variable
```{r, eval=FALSE}
x <- scan("Thisismytextfile.txt", what=character)
xtext <- read.delim(thisismytextfile.txt)

DATA_DIR <- system.file("extdata/", package = "readtext")

x <- read.csv(file=Thisismytextfile.csv, header=FALSE)

```

### Problem 19 
Output the contents of a variable to a .txt file
```{r, eval=FALSE}
a <- write.csv(Thisismytextfile.csv)
```

### Problem 20 
Create a variable that stores a 20x20 matrix of random numbers
```{r}
a <- matrix(runif(20), ncol=20,nrow=20)
```

### Problem 21
Output any matrix to a txt file using commas or tabs to separate column values, and new lines to separate row values
```{r}
b <-write.csv(a)
```

















