---
title: "Graph Work"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 1
    #code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```

```{r}
library(ggplot2)
```


### Cao et al. (2019)
```{r}
# Create dataframe
a <- c(runif(8,0,70))
b <- c(runif(8,0,70))
plot_df <- data.frame(a,b)

# basic scatterplot
ggplot(plot_df, aes(x=a,y=b))+
  geom_point()+
  geom_smooth(method=lm)+
  coord_cartesian(xlim=c(0,70),ylim=c(0,70))+
  xlab("Average Frequency of Nonsocial Risk")+
  ylab("Average Frequency of Social Risk")+
  theme_classic(base_size=12)
  
#Questions: how do you get rid of grey area, change the formatting of the line? Asking these questions
```

### Jeffereies (2019)
```{r, eval=FALSE}

Evalofperson <- c(runif(10,0,7))
P_Target <- c(runif(10,0,1))
Gender <- rep(c("M","W"),5)

plot_df <- data.frame(Evalofperson,P_Target,Gender)

# basic scatterplot
library(ggplot2)
ggplot(plot_df, aes(Evalofperson, P_Target, shape=Gender, colour=Gender, fill=Gender))+
    geom_point(size=3)+
    geom_smooth(method=lm)+
    coord_cartesian(xlim=c(0,7),ylim=c(0,1))+
    xlab("Evaluation of Person X")+
    ylab("P(Target=Pilot)")+
    theme_classic(base_size=12)+
    facet_wrap(~factor_three)
```
```{r}
library(ggplot2)
evaluation<-c((seq(1,7,.1)+runif(61,-2,2)),
              (seq(1,7,.1)+runif(61,-2,2)))
pTarget <-c((seq(.92,.85,length.out=61)+runif(61,-.1,.1)),
            (seq(.8,.4,length.out=61)+runif(61,-.5,.5)))
Gender <- rep(c("Man Communicated with ATC",
            "Woman Communicated with ATC"), each=61)
plot_df<-data.frame(evaluation,pTarget,Gender)
ggplot(plot_df, aes(x=evaluation,y=pTarget,
                    group=Gender,
                    color=Gender))+
  geom_smooth(method="lm")+
  theme_classic()+
  scale_y_continuous(breaks=seq(0,1,.1),labels = scales::percent)+
  scale_x_continuous(breaks=seq(1,7,1))+
  coord_cartesian(ylim=c(0,1))+
  xlab("Evaluation of Person X")+
  ylab("P(Target = Pilot)")+
  theme(legend.position=c(0.45,0.2),
        legend.title=element_blank(),
        legend.key.size = unit(.5, "cm"))+
  theme(legend.key = element_rect(colour = 'white', fill = 'white', size = 1, linetype='solid'))
```
```


### Kim et al. (2019)
```{r}
a <- c(runif(20,-2.5,5))
b <- c(runif(20,-20,30))
plot_df <- data.frame(a,b)

#Empathy
ggplot(plot_df, aes(x=a,y=b))+
  geom_point()+
  geom_smooth(method=lm)+
  coord_cartesian(xlim=c(-2.5,5),ylim=c(-20,30))+
  xlab("Social N400")+
  ylab("Empathy Quotient Test")

#Reading in the Mind
c <- c(runif(20,-2.5,5))
d <- c(runif(20,-8,8))
plot_df2 <- data.frame(c,d)

ggplot(plot_df2, aes(x=c,y=d))+
  geom_point()+
  geom_smooth(method=lm)+
  coord_cartesian(xlim=c(-2.5,5),ylim=c(-8,8))+
  xlab("Social N400")+
  ylab("Reading the Mind in the Eyes Test")

#Autism Spectrum Quotient 
e <- c(runif(20,-2.5,5))
f <- c(runif(20,-10,20))
plot_df3 <- data.frame(e,f)

ggplot(plot_df3, aes(x=e,y=f))+
  geom_point()+
  geom_smooth(method=lm)+
  coord_cartesian(xlim=c(-2.5,5),ylim=c(-10,20))+
  xlab("Social N400")+
  ylab("Autism Spectrum Quotient")
```



### Jouravlev et al (2019)
```{r}
factor_one <- rep(as.factor(c("No Transient","Transient")),2)
factor_two <- rep(as.factor(c("Outside","Inside")),2)
factor_three <- rep(as.factor(c("Visual Group","Auditory Group")),each=4)
dv_means <- c(305,302,290,275)
dv_SEs   <- c(4,3.4,4,3)
plot_df <- data.frame(factor_one,
                      factor_two,
                      factor_three,
                      dv_means,
                      dv_SEs)

# basic bar graph

ggplot(plot_df, aes(x=factor_one,y=dv_means,
                    group=factor_two,
                    color=factor_two))+
  geom_bar(stat="identity", position="dodge")+
  facet_wrap(~factor_three)+
  theme_classic(base_size=12)+
  xlab("Condition")+
  ylab("Mean Mediant RT (ms)")
```

