---
title: "Hard Problems"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 1
    #code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```

### Problem 1
The FizzBuzz Problem. List the numbers from 1 to 100 with the following constraints. If the number can be divided by three evenly, then print Fizz instead of the number. If the number can be divided by five evenly, then print Buzz instead of the number. Finally, if the number can be divided by three and five evenly, then print FizzBuzz instead of the number. 
```{r} 

number <- c(1:100)

for (i in 1:100){
  if (number%%3==0) {
  number[i] <- "Fizz"
  }
  if (number%%5==0){
    number[i] <- "Buzz"
  }
  if (number%%4 == 0 & a%%8 ==0) {
    number[i] <- "FizzBuzz"
  }
  else {
    number[i] <- a
  }
}


#for(a in 1:100) {
   #if (a%%3==0) {
     x(a) <- Fizz
 

#if (a(z)%%3==0)
  a<-Fizz
#if (a(z)%%5==0)
  a<-Buzz
#if (a(z)%%3==0)&(a(z)%%5==0)
  a<-FizzBuzz
```

### Problem 2
Frequency Counts Take text as input, and be able to produce a table that shows the counts for each character in the text. This problem is related to the earlier easy problem asking you to count the number of times that a single letter appears in a text. The slightly harder problem is the more general version: count the frequencies of all unique characters in a text.
```{r}
a<-"this is my sentence"
table(unlist(strsplit(a,split="")))
```

### Problem 3
Test the Random Number Generator Test the random number generator for a flat distribution. Generate a few million random numbers between 0 and 100. Count the number of 0s, 1s, 2s, 3s, etc. all the way up to 100. Look at the counts for each of the numbers and determine if they are relatively equal. For example, you could plot the counts in Excel to make a histogram. If all of the bars are close to being flat, then each number had an equal chance of being selected, and the random number generator is working without bias.
```{r, eval=FALSE}
d<-runif(1,100,1)
x<- count.fields(d)
hist(x)
```

### Problem 4
Create a multiplication table Generate a matrix for a multiplication table. For example, the labels for the columns could be the numbers 1 to 10, and the labels for the rows could be the numbers 1 to 10. The contents of each of the cells in the matrix should be correct answer for multiplying the column value by the row value.
```{r}
num = as.integer(readline(prompt = "Enter a number: "))
# use for loop to iterate 10 times
for(i in 1:10) {
print(paste(num,'x', i, '=', num*i))
}
```

### Problem 5
Encrypt and Decrypt the Alphabet Turn any normal english text into an encrypted version of the text, and be able to turn any decrypted text back into normal english text. A simple encryption would be to scramble the alphabet such that each letter corresponds to a new randomly chosen (but unique) letter.
```{r}

```

### Problem 6 
Snakes and Ladders

### Problem 7
Assume that a pair of dice are rolled. Using monte carlo-simulation, compute the probabilities of rolling a 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, and 12, respectively.
```{r}
X = matrix(ncol = 4,nrow = 10000)
for(year in 1:4) {
# for each year sample the return 10000 times
 for(i in 1:10000){
  X[i,year] = sample(returns,1)
 }
}

# show first 6 rows
head(X)
```

### Problem 8
Monte Hall Problem
```{r}
rm(list=ls())
monty<-function(strat='stay',N=1000,print_games=TRUE)
{
 doors<-1:3 #initialize the doors behind one of which is a good prize
 win<-0 #to keep track of number of wins
 
for(i in 1:N)
 {
 prize<-floor(runif(1,1,4)) #randomize which door has the good prize
 guess<-floor(runif(1,1,4)) #guess a door at random
 
## Reveal one of the doors you didn't pick which has a bum prize
 if(prize!=guess)
 reveal<-doors[-c(prize,guess)]
 else
 reveal<-sample(doors[-c(prize,guess)],1)
 
 ## Stay with your initial guess or switch
 if(strat=='switch')
 select<-doors[-c(reveal,guess)]
 if(strat=='stay')
 select<-guess
 if(strat=='random')
 select<-sample(doors[-reveal],1)
 
## Count up your wins
 if(select==prize)
 {
 win<-win+1
 outcome<-'Winner!'
 }else
 outcome<-'Losser!'
 
if(print_games)
 cat(paste('Guess: ',guess,
 '\nRevealed: ',reveal,
 '\nSelection: ',select,
 '\nPrize door: ',prize,
 '\n',outcome,'\n\n',sep=''))
 }
 cat(paste('Using the ',strat,' strategy, your win percentage was ',win/N*100,'%\n',sep='')) #Print the win percentage of your strategy
}
```

