---
title: "Journal"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 1
    #code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```

### Problem 1

Do simple math with numbers, addition, subtraction, multiplication, division

```{r}

1+1
6-5
9*0
10/5

```
### Problem 2

Put numbers into variables, do simple math on the variables 

```{r, eval=FALSE}

a <- 1
b <- 3

a+b
b-a
a*b
b/a

c <- 5

a+b+c
```
### Problem 3
Write code that will place the numbers 1 to 100 separately into a variable using for loop. Then, again using the seq function.

```{r}



```

### Problem 12
Count the number of words in a string variable

```{r}
a <- "count the number of words in this sentence"

b <- strsplit(a, split=" ")

length(b[[1]])

```

### Problem 13 
Count the number of sentences in a string variable

```{r}
a <- "This is one sentence. This is another sentence as well. Here is the third sentence. But wait there is also a fourth sentence."

b <- strsplit(a, split="[.]")

length(b[[1]])

```

### Problem 14
Count the number of times a specific character occurs in a string variable

```{r}
a <- "abcabbccaaabbbbc"

b <- strsplit(a, split="a")

length(b[[1]])
```




















