---
title: "R Functions"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 1
    #code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```

## The assignment
I’ve selected numerous functions from the above two sources, and I am listing them below under different categories. Your job is to create an .rmd file to add to your webpage. In this file you will copy the list of function names below. For each one, give a brief description of what it does, and then write a code-chunk demonstrating that you can use the function.

###List of functions

### ***General bits***
1.	help(topic)
-This function helps to find info about the another R function. Simply put the function in the parenthesis and it will pull up info.
```{r}
help("mean")
```
2.	?topic
-This function is similar to help
```{r}
?mean
```
3.	ls()
-Return a vector of character strings giving the names of the objects in the specified environment.
```{r}
?ls

```
4.	dir()
-These functions produce a character vector of the names of files or directories in the named directory.
```{r}
?dir
```
5.	list.files()
-These functions produce a character vector of the names of files or directories in the named directory.
```{r}
?list.files()
```

### ***Input and output***
1.	save()
-Writes an external representation of R objects to the specified file. 
```{r}
?save

```
2.	load()
-Reload datasets written with the function save.
```{r}
?load
```
3.	data()
-Loads specified data sets, or list the available data sets.
```{r}
?data()
```
4.	library()
5.	read.table()
6.	read.csv()
7.	scan()
8.	print()
9.	cat()
10.	write.table()
 
### Data Creation
1.	c()
-This is a generic function which combines its arguments.
```{r}
a <- c(1,2,3,4,5)
```

2.	from:to (where from and to are replaced with numbers, e.g. 1:10)

3.	seq()
-Generate regular sequences. seq is a standard generic with a default method
```{r}
b <- seq(1:5)
```
4.	rep()
-Replicates the values in x. It is a generic function

5.	data.frame()
The function data.frame() creates data frames, tightly coupled collections of variables which share many of the properties of matrices and of lists, used as the fundamental data structure by most of R's modeling software

6.	list()
-Functions to construct, coerce and check for both kinds of R lists.
```{r}
?list
```
7.	matrix()
-Matrix creates a matrix from the given set of values.
```{r}
M <- matrix(c(1:10), nrow = 3, byrow = TRUE)
```
8.	factor()
-The function factor is used to encode a vector as a factor (the terms ‘category’ and ‘enumerated type’ are also used for factors). If argument ordered is TRUE, the factor levels are assumed to be ordered. For compatibility with S there is also a function ordered.

9.	rbind()
-Take a sequence of vector, matrix or data-frame arguments and combine by columns or rows, respectively

10.	cbind()
-Take a sequence of vector, matrix or data-frame arguments and combine by columns or rows, respectively.`

### Slicing and extracting data
### ***Indexing vectors***
1.	x[n] nth element

2.	x[-n] all but nth element

3.	x[1:n] first n elements

4.	x[-(1:n)] elements from n+1 to the end

5.	x[c(1,4,2)] specific elements

6.	x[“name”] elements named “name”

7.	x[x>3] all elements greater than 3

8.	x[x > 3 & x < 5] all elements between 3 and 5

9.	x[x %in% c(“a”,“and”,“the”)] all elements in given set

### ***Indexing lists***
1.	x[n] list with elements n
2.	x[[n]] nt h element of the list
3.	x[[“name”]] element of the list named “name”
4.	x$name id.

### ***Indexing matrices***
1.	x[i,j] element at row i, column j
2.	x[i,] row i
3.	x[,j] column j
4.	x[,c(1,3)] columns 1 and 3
5.	x[“name”,] row named “name”

### ***Indexing data frames (matrix indexing plus the following)***
1.	x[[“name”]] column named “name”
2.	x$nameid.

### Variable conversion
1.	as.data.frame(x)

2.	as.numeric(x)

3.	as.logical(x)

4.	as.character(x)

### Variable information
1.	is.na(x)
-NA is a logical constant of length 1 which contains a missing value indicator. NA can be coerced to any other vector type except raw. There are also constants NA_integer_, NA_real_, NA_complex_ and NA_character_ of the other atomic vector types which support missing values: all of these are reserved words in the R language.
```{r}
?is.na()
```
2.	is.null(x)

3.	is.data.frame(x)

4.	is.numeric(x)

5.	is.character(x)
-This function

6.	length(x)
-This function definds the size of a vector 
```{r}
x <- c(1,2,3,4,5)

b <- length(x)
```

7.	dim(x)
-This function definds the dimentnions of an object

8.	dimnames(x)
-Retrieve or set the dimnames of an object.

9.	nrow(x)
-Returns the number of rows present in a matrix

10.	ncol(x)
-Returns the number of columns present in a matrix 

11.	class()
-This functions tells the class type the data belongs to

12.	attributes()
-These functions access an object's attributes. The first form below returns the object's attribute list. The replacement forms uses the list on the right-hand side of the assignment as the object's attributes (if appropriate).

### Data selection and manipulation
1.	which.max()
-Determines the location, i.e., index of the (first) minimum or maximum of a numeric (or logical) vector
```{r}
?which.max
```
2.	which.min()
-Determines the location, i.e., index of the (first) minimum or maximum of a numeric (or logical) vector.
```{r}
?which.min
```
3.	which()
-Give the TRUE indices of a logical object, allowing for array indices.
```{r}
?which
```
4.	sort()
-Sort (or order) a vector or factor (partially) into ascending or descending order. For ordering along more than one variable
```{r}
?sort
```
5.	unique()
-Returns a vector, data frame or array like x but with duplicate elements/rows removed.
```{r}
?unique()
```
6.	table()
-Uses the cross-classifying factors to build a contingency table of the counts at each combination of factor levels.
```{r}
?table
```
7.	sample()
-Takes a sample of the specified size from the elements of x using either with or without replacement.
```{r}
?sample
```

### Math
1.	max()
-Finds the max of a data set 
```{r}
?max

c <-max(x)
```
2.	min()
-Finds the min of a data set 
```{r}
d <- min(x)
```
3.	range()
-Finds the range of a data set 
```{r}
e <- range(x)
```
4.	sum()
-Finds the sum of a data set 
```{r}
t <-sum(x)
```
5.	mean()
-Finds the average of a data set 
```{r}
f <- mean(x)
```
6.	median()
-Finds the median of a data set 
```{r}
g <- median(x)
```
7.	var()
-Finds the variance of a data set 
```{r}
h <- var(x)
```
8.	sd()
-Finds the standard devaition of a data set
```{r}
u <- sd(x)
```
9.	cor()
-Var, cov and cor compute the variance of x and the covariance or correlation of x and y if these are vectors
```{r}
?cor
```
10.	round()
-Rounds the numbers in the data set 
```{r}

x <- c(2.7,4.9,6.1,8.5)
a <- round(x)
  
```
11.	abs()
```{r}
y <- c(-1,-10,2,4)
b <- abs(y)
```

### Matrices
1.	t()
2.	diag()
3.	rowSums()
4.	colSums()
5.	rowMeans()
6.	colMeans()

### Advanced Data processing
1.	apply()
2.	aggregate()
Strings
1.	paste()
2.	strsplit()
3.	tolower()
4.	toupper
Plotting
1.	hist()
2.	plot()
Distributions
1.	rnorm()
2.	runif()

### Programming
1.	show that you can define a function

2.	show that you can write a for loop

3.	show that you can write a while loop

4.	show that you can write an if else statement

5.	Explain what return() does inside a function, show you can use it
-Gets the number out of the function. Tells the function to output

6.	Explain what break() does, show you can use it


###Installing some packages
Use the packages tab in R-studio to install these packages. You will need to be connected to the internet when you do this. If you are installing on your laptop, or on R-studio Cloud, then these packages will not need to installed again.

1.	ggplot2
-Create elegant data visualations using the grammar of graphics

2.	dplyr
-Grammar of data manipulation

3.	shiny
-Web application framework for R

4.	data.table

5.	reshape2
-Reshapes data

6.	stringr
-Wrappers for common string operations


