---
title: "Image Processing in R"
subtitle: "wth *imager*"
author: "Ana-Louise Franz"
output:
  xaringan::moon_reader:
    css: [default, metropolis, metropolis-fonts]
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---
class: inverse, center, middle

# Before Loading *imager*

---

class: middle

## XQuartz

- Before loading imager, "XQuartz" had to be installed

--

- "Apple created the XQuartz project as a community effort to further develop and support X11 on Mac."

--

- https://www.xquartz.org

---
class: inverse, center, middle

# Using *imager*

---

class: middle

## Loading *imager*

--

- The package must be installed from CRAN 

--

- The package must then be loaded using:


```{r, results='hide',message=FALSE}

library(imager)

```

---

## Pre-loaded Images in *imager*

--

```{r, results='hide', message=FALSE, fig.align='center', fig.height=5.5}

plot(boats)
```

---

## Getting Info About Images

--

```{r}
boats
```

--

- Image information is as numeric imager-array

--
- You can do math using the image

--
```{r}
mean(boats)
```

---
## *Imager* Math in Pictures

--

```{r, results='hide', message=FALSE, fig.align='center', fig.height=5.5}

layout(t(1:2))
plot(boats,rescale=FALSE)
plot(boats/2,rescale=FALSE)
```

---
## Changing Picture Colors
--
```{r}
rgb(0,1,0)
```
--
```{r, results='hide', message=FALSE, fig.align='center', fig.height=4.75}

cscale <- function(r,g,b) rgb(g,r,b)
plot(boats,colourscale=cscale,rescale=FALSE)
```

---

## Loading Your Own Images

--
```{r, results='hide', message=FALSE, fig.align='center', fig.height=4.75}

fpath <- system.file('extdata/Leonardo_Birds.jpg',package='imager') 
birds <- load.image(fpath)
plot(birds)

```

---
## Loading Your Own Images

```{r, results='hide', message=FALSE, fig.align='center', fig.height=4.75}

layout(t(1:2))
plot(birds,rescale=FALSE)
plot(birds/2,rescale=FALSE)
```

---
class: middle 
## Just The Beginning

- Many more things can be done in *imager*

--

- Loading multiple pictures at once 

--

- Loading videos 

--

- Graphing color orientation

---
class: inverse, middle, center

# THE END

```{r, eval=FALSE}
load.image(www.pngonly.com/wp-content/uploads/2017/06/Nature-Flowers-PNG-Image.png)
```

